### 2018-12-21 tex/paper.tex
Higher-order diversity section modified.

\begin{figure*}
    \centering
\begin{tabular}{cccccc}
        \includegraphics[scale = 0.14]{\imagePath/stereo/venus_GT} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/venus_left_mf} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/venus_left_submod} &
    %
        \includegraphics[scale = 0.19]{\imagePath/stereo/tsukuba_GT} &
        \includegraphics[scale = 0.19]{\imagePath/stereo/potts/tsukuba_left_mf} &
        \includegraphics[scale = 0.19]{\imagePath/stereo/potts/tsukuba_left_submod} \\
        \scriptsize(a) Venus GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution & \scriptsize(a) Tsukuba GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution\\
        {} & \scriptsize  60.32s, 1.83e+07 &  \scriptsize 469.75s, {\bf 1.55e+07} & {} & \scriptsize  14.93s, 8.21e+06 & \scriptsize 215.22s, {\bf 4.12e+06} \\
         \includegraphics[scale = 0.14]{\imagePath/stereo/cones_GT} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/cones_left_mf} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/cones_left_submod} &
        %
       %
         \includegraphics[scale = 0.15]{\imagePath/stereo/teddy_GT} &
        \includegraphics[scale = 0.15]{\imagePath/stereo/potts/teddy_left_mf} &
        \includegraphics[scale = 0.15]{\imagePath/stereo/potts/teddy_left_submod} \\
    \scriptsize(a) Cones GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution & \scriptsize(a) Teddy GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution\\
        {} & \scriptsize 239.14s, 2.68e+07 &  \scriptsize 1082.72s, {\bf 1.27e+07} & {} & \scriptsize 555.30s, 2.36e+07 & \scriptsize 1257.86s, {\bf 1.58e+07}\\
\end{tabular}
%\vspace{2mm}
\mycaption{\footnotesize \em Stereo matching using dense CRFs with Potts
compatibility and Gaussian pairwise potentials. We compare our solution with
the mean-field algorithm of Koltun and Krahenbuhl \citep{koltun2011efficient}. We observe that our method gives better-looking solutions with lower energy value at the cost of higher computational time.}
\label{fig:stereo}
\end{figure*}

@@

\begin{figure*}
    \centering
\begin{tabular}{cccccc}
        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_GT} &
        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_hop} &
        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/baby1_GT} &
        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/baby1_hop} &
        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/flowerpots_GT} &
        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/flowerpots_hop} \\
        \scriptsize(a) Tsukuba GT & \scriptsize(b) Submod solution
        & \scriptsize(a) Baby1 GT & \scriptsize(b) Submod solution
        & \scriptsize(a) Flowerpots GT & \scriptsize(b) Submod solution\\
        {} & {} 
        & {} & \scriptsize 2476.82s
        & {} & \scriptsize 2471.58s\\

\end{tabular}
%\vspace{2mm}
\mycaption{\footnotesize \em Stereo matching using dense CRFs with higher-order
  Potts term in addition to Potts compatibility and Gaussian pairwise potentials.}
\label{fig:stereo_hop}
\end{figure*}

%\mysubsection{Stereo Matching using Higher-order Potts Model}
%\label{subsec:stereo_hop}
%\myparagraph{Data} Next, we use the higher-order Potts model for stereo matching on the Middlebury dataset. Higher-order Potts model is suitable to be used for only some images in the dataset, since others have gradually sloping surfaces and higher-order cliques will force all pixels on these surfaces to take similar disparity values.  We take a dense CRF model with Potts compatibility term and Gaussian pairwise potentials, and augment it with higher-order Potts term. We obtain higher-order cliques by using super-pixels obtained from mean-shift algorithm \citep{comaniciu2002mean}.
%
%\myparagraph{Method} We again use the modified Gaussian filtering implementation for dense CRFs by
%\citep{ajanthan2017efficient} to compute the conditional gradient at each step.
%To compute the contribution of the higher-order Potts, we make use of an
%efficient strategy to reuse computation. Recall that computing the conditional
%gradient coordinates $s^*_{\sigma(i)}$ requires us to obtain differences of the
%nested sets $F(S_i) - F(S_{i - 1})$. We store the clique state at each $i$, and
%this enables us to compute the difference for each coordinate in a constant
%amount of time. In this case, computation of conditional gradient takes
%$\mathcal{O}(cNL)$ where $c$ is the number of higher-order cliques. We ran our
%algorithm for 200 iterations.
%
%\myparagraph{Results} Figure \ref{fig:stereo_hop} shows some example solutions
%obtained by picking the label with maximum marginal probability for each
%variable. We observe that our method gives results that are reasonably close to
%the ground-truth. The set of hyperparameters that we used can be found in the
%appendix.

>>>>

\begin{figure*}
    \centering
\begin{tabular}{ccc}
        \includegraphics[scale = 0.24]{\imagePath/stereo/venus_GT} &
        \includegraphics[scale = 0.24]{\imagePath/stereo/potts/venus_left_mf} &
        \includegraphics[scale = 0.24]{\imagePath/stereo/potts/venus_left_submod} \\
    %
        \scriptsize(a) Venus GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution \\ 
        {} & \scriptsize  60.32s, 1.83e+07 &  \scriptsize 469.75s, {\bf 1.55e+07}  \\
        \includegraphics[scale = 0.27]{\imagePath/stereo/tsukuba_GT} &
        \includegraphics[scale = 0.27]{\imagePath/stereo/potts/tsukuba_left_mf} &
        \includegraphics[scale = 0.27]{\imagePath/stereo/potts/tsukuba_left_submod} \\
        \scriptsize(a) Tsukuba GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution\\
        {} & \scriptsize  14.93s, 8.21e+06 & \scriptsize 215.22s, {\bf 4.12e+06} \\

        \includegraphics[scale = 0.24]{\imagePath/stereo/cones_GT} &
        \includegraphics[scale = 0.24]{\imagePath/stereo/potts/cones_left_mf} &
        \includegraphics[scale = 0.24]{\imagePath/stereo/potts/cones_left_submod} \\
        \scriptsize(a) Cones GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution \\
        {} & \scriptsize 239.14s, 2.68e+07 &  \scriptsize 1082.72s, {\bf 1.27e+07} \\ 
        %
       %
         \includegraphics[scale = 0.25]{\imagePath/stereo/teddy_GT} &
        \includegraphics[scale = 0.25]{\imagePath/stereo/potts/teddy_left_mf} &
        \includegraphics[scale = 0.25]{\imagePath/stereo/potts/teddy_left_submod} \\
        \scriptsize(a) Teddy GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution\\
        {} & \scriptsize 555.30s, 2.36e+07 & \scriptsize 1257.86s, {\bf 1.58e+07}\\
\end{tabular}
%\vspace{2mm}
\mycaption{\footnotesize \em Stereo matching using dense CRFs with Potts
compatibility and Gaussian pairwise potentials. We compare our solution with
the mean-field algorithm of Koltun and Krahenbuhl \citep{koltun2011efficient}. We observe that our method gives better-looking solutions with lower energy value at the cost of higher computational time.}
\label{fig:stereo}
\end{figure*}

@@

%\begin{figure*}
%    \centering
%\begin{tabular}{cccccc}
%        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_GT} &
%        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_hop} &
%        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/baby1_GT} &
%        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/baby1_hop} &
%        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/flowerpots_GT} &
%        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/flowerpots_hop} \\
%        \scriptsize(a) Tsukuba GT & \scriptsize(b) Submod solution
%        & \scriptsize(a) Baby1 GT & \scriptsize(b) Submod solution
%        & \scriptsize(a) Flowerpots GT & \scriptsize(b) Submod solution\\
%        {} & {} 
%        & {} & \scriptsize 2476.82s
%        & {} & \scriptsize 2471.58s\\
%
%\end{tabular}
%%\vspace{2mm}
%\mycaption{\footnotesize \em Stereo matching using dense CRFs with higher-order
%  Potts term in addition to Potts compatibility and Gaussian pairwise potentials.}
%\label{fig:stereo_hop}
%\end{figure*}
%
%\mysubsection{Stereo Matching using Higher-order Diversity Model}
%\label{subsec:stereo_hop}
%\myparagraph{Data} Next, we use the higher-order diversity model for stereo matching on the Middlebury dataset. Higher-order Potts model is suitable to be used for only some images in the dataset, since others have gradually sloping surfaces and higher-order cliques will force all pixels on these surfaces to take similar disparity values.  We take a dense CRF model with Potts compatibility term and Gaussian pairwise potentials, and augment it with higher-order Potts term. We obtain higher-order cliques by using super-pixels obtained from mean-shift algorithm \citep{comaniciu2002mean}.
%
%\myparagraph{Method} We again use the modified Gaussian filtering implementation for dense CRFs by
%\citep{ajanthan2017efficient} to compute the conditional gradient at each step.
%To compute the contribution of the higher-order Potts, we make use of an
%efficient strategy to reuse computation. Recall that computing the conditional
%gradient coordinates $s^*_{\sigma(i)}$ requires us to obtain differences of the
%nested sets $F(S_i) - F(S_{i - 1})$. We store the clique state at each $i$, and
%this enables us to compute the difference for each coordinate in a constant
%amount of time. In this case, computation of conditional gradient takes
%$\mathcal{O}(cNL)$ where $c$ is the number of higher-order cliques. We ran our
%algorithm for 200 iterations.
%
%\myparagraph{Results} Figure \ref{fig:stereo_hop} shows some example solutions
%obtained by picking the label with maximum marginal probability for each
%variable. We observe that our method gives results that are reasonably close to
%the ground-truth. The set of hyperparameters that we used can be found in the
%appendix.

\mysubsection{Stereo Matching using Higher-order Diversity Model}
TO-DO

\mysubsection{Stereo Matching using Higher-order Diversity Model}
TO-DO
